Topic Scores

### 2019-02-28 Topic Scores.Rmd
change name of file

rm(lists, d_AoD, d_assessment, d_ILO)
```
##Models in list:
```{r models in list}
LDA_models <- list()
LDA_models$description <- LDA_description_35
LDA_models$overview <- LDA_overview_35
LDA_models$manual <- LDA_manual_40

@@

### Saving files for APP
```{r keywords}
save(distribution, kw, course_all, course_following_semester,
     file = "App/Recommender System/topic_model.RDATA")
```

>>>>

rm(lists, d_AoD, d_assessment, d_ILO)
```

##Models in list:
```{r models in list}
LDA_models <- list()
LDA_models$description <- LDA_description_35
LDA_models$overview <- LDA_overview_35
LDA_models$manual <- LDA_manual_40

@@

### Saving files for APP
```{r keywords}
save(distribution, kw, course_all, course_following_semester,
     file = "App/Recommender System/data_topic_models.RDATA")
```
